Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-01-28 RET_Hosts.tex

There are a limited number of local analogues to the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.]{Prentice2019,Lyman2019,Perley2019}. The transient declined from its discovery, with constraints on a ~1 day rise time, and did not resemble any known SN, GRB afterglow, or kilonova (KN). 
Other nearby rapid transients include the local fast-declining SN Ibn SN2018kzr \citep{McBrien2020}, and KSN-2015K \citep{Rest2018}. It is currently unclear whether these transients

In this paper, we present the first comprehensive study of the host galaxies of rapidly evolving transients. We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques. Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe.

>>>>

There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}. The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN) \citep{Ho2019}. There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN) \citep{Soker2019}
Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf in a non-standard scenario, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.

In this paper, we present the first comprehensive study of the host galaxies of rapidly evolving transients. We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques. Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients. For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
